An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-25 poly-embed-journal/poly-embed-journal.tex
a few more tweaks

\begin{proposition}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link}$(L,\ell,\epsilon,\|\cdot\|_\infty)$.
  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
\end{proposition}
\begin{proof}
  For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
  By definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R ~:~ \phi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
  By definition of embedding, $R_p = \gamma(p)$.
  By definition of separation, a link $\psi$ is $\epsilon$-separated if and only if, for all $u$, $\psi(u) \in \cap_{p \in P_u} \gamma(p) = \Psi(u)$.
\raft{Looks great/close, but I got lost with the ``if and only if, then'' \bo{updated, how about now?}}
\end{proof}

@@

%\botodo{Should we comment on computing the $\epsilon$?}
%\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
\botodo{Not sure if we have anything useful to say on computing $\epsilon$}

@@

\begin{figure}
	\begin{minipage}{0.3\linewidth}
    \input{tikz/abstain-intuition}
    \raf{Let's add $p,p'$ to the figure.  Otherwise, really nice job!}
\end{minipage}
\begin{minipage}{0.7\linewidth}
	\caption{The BEP surrogate $L$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
	The level sets of $\Gamma := \prop{L}$ are given in solid black lines, while the level sets of $\mode$ are given in dashed blue lines.
	To demonstrate non-calibration, one can pick distributions $p, p'$ in the relative interior of the abstain cell (blue) but in different cells of the mode.
  These distributions will satisfy $\Gamma(p) = \Gamma(p')$ but $\mode(p) \neq \mode(p')$.
  In this case, fixing $u\in\Gamma(p)$, it is impossible to define $\psi(u)$ to satisfy calibration, as $\psi(u)$ cannot be equal to $\mode(p)$ and $\mode(p')$ simultaneously.
  In particular, even though $u$ is $L$-optimal for both $p$ and $p'$, it will be $\ell$-suboptimal for at least one, violating calibration.
  We may impose restrictions on the conditional label distributions to remove the blue cell, however, and thus satisfy calibration.
  For this example, the BEP surrogate is classification-calibrated if one restricts to the set of distributions where at least one label $y\in\Y$ has probability $p_y \geq \tfrac 1 2$.
	}
	\label{fig:abstain-intuition-inconsistent}
	\end{minipage}
\end{figure}

>>>>

\begin{proposition}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link}$(L,\ell,\epsilon,\|\cdot\|_\infty)$.
  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
\end{proposition}
\begin{proof}
  For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
  By definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R : \varphi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
  By definition of embedding, $R_p = \gamma(p)$.
  By definition of separation, a link $\psi$ is $\epsilon$-separated if and only if, for all $u$, $\psi(u) \in \cap_{p \in P_u} \gamma(p) = \Psi(u)$.
\raft{Looks great/close, but I got lost with the ``if and only if, then'' \bo{updated, how about now?}\raf{That part is great now, but I'm worried about $R_p = \gamma(p)$ and wonder if we should step through that slower. Actually maybe this is an issue with the construction itself: I think you only want to work with the representative set from the definition of embedding, right?}}
\end{proof}

@@

%\botodo{Should we comment on computing the $\epsilon$?}
%\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
\botodo{Not sure if we have anything useful to say on computing $\epsilon$}
\raft{Agreed}

@@

\begin{figure}
	\begin{minipage}{0.3\linewidth}
    \input{tikz/abstain-intuition}
\end{minipage}
\begin{minipage}{0.7\linewidth}
	\caption{The BEP surrogate $L$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
	The level sets of $\Gamma := \prop{L}$ are given in solid black lines, while the level sets of $\mode$ are given in dashed blue lines.
	To demonstrate non-calibration, one can pick distributions $p, p'$ in the relative interior of the abstain cell (blue) but in different cells of the mode.
  These distributions will satisfy $\Gamma(p) = \Gamma(p')$ but $\mode(p) \neq \mode(p')$.
  In this case, fixing $u\in\Gamma(p)$, it is impossible to define $\psi(u)$ to satisfy calibration, as $\psi(u)$ cannot be equal to $\mode(p)$ and $\mode(p')$ simultaneously.
  In particular, even though $u$ is $L$-optimal for both $p$ and $p'$, it will be $\ell$-suboptimal for at least one, violating calibration.
  We may impose restrictions on the conditional label distributions to remove the blue cell, however, and thus satisfy calibration.
  For this example, the BEP surrogate is classification-calibrated if one restricts to the set of distributions where at least one label $y\in\Y$ has probability $p_y \geq \tfrac 1 2$.
	}
	\label{fig:abstain-intuition-inconsistent}
	\end{minipage}
\end{figure}
